Lord Vorotron: Finding the Best JFA Variant for the Coming Winter

### 2020-09-18 paper/main.tex
square|star+noise
new domains and tactic for space search

% kollektiv
% https://www.youtube.com/watch?v=E8g5YrDXg2k
% go with the flow
% https://www.youtube.com/watch?v=DcHKOC64KnE
% private party project
% https://www.youtube.com/watch?v=ckKi01gqW7A&t=878s
% royal blood
% https://www.youtube.com/watch?v=sbx95gBb5HM
% i don't want to sleep
% https://www.youtube.com/watch?v=3oBCu9zywzE
% hehe
% https://www.youtube.com/watch?v=Dii8ZVtR9Tc&t=18s

@@

%%% BONUS %%%
%\usepackage[table]{xcolor}  % for colors (like `red`)
\usepackage[normalem]{ulem} % for underline
\usepackage{booktabs}       % for better table
\usepackage{bm}             % for special table cell (`cellcolor`)
\usepackage{hhline,soul}    % for `hl` command (highlight text)
\usepackage{amsmath}        % for multi-line math
\usepackage[bottom]{footmisc}% for footnotes
\usepackage{tabularx, booktabs}
\newcolumntype{L}{>{\raggedright\footnotesize}m{5.75cm}}
\renewcommand{\arraystretch}{1.2}
%%%%%%%%%%%%%

@@

\begin{table}[H] \centering
\begin{tabular}{@{}lllll@{}}
\toprule
Reference                & Algorithm    & Exactness   & Time         & Work         \\ \midrule
\citep{de2017fast}       & FastGPU      & Exact       & $O(n^3/p)$   & -            \\
\citep{cao2010parallel}  & PBA          & Exact       & $O(n)$       & $O(mN)$      \\
\citep{honda2017simple}  & based on SKW & Exact       & $O(n)$       & $O(N)$       \\
\citep{manduhu2019work}  & WTO          & \cellcolor{blue!25}\textbf{Exact}&
	\cellcolor{blue!25}$\mathbf{O(\log n)}$  & $O(N)$       \\
\citep{schneider2009gpu} & SKW          & Approximate & $O(n)$       & $O(N)$       \\
\citep{rong2006jump}     & JFA          & Approximate & $O(\log n)$  & $O(N\log n)$ \\ \bottomrule
In this paper            & \ourjfasingle&
	\cellcolor{blue!25}\textbf{Approximate} &
	\cellcolor{blue!25}$\sim$$\mathbf{O(\log^{\ast} n)}$ & $\sim$$O(N)$ \\
                         & \ourjfa      &
	\cellcolor{blue!25}\textbf{Approximate} &
	\cellcolor{blue!25}$\sim$$\mathbf{O(1)}$ & $\sim$$O(N)$ \\
\bottomrule
\end{tabular}
\vspace{1em}
\caption{Different GPU algorithms for computing EDT}
\end{table}

@@

@@

@@

@@

\begin{itemize}
	\item \textbf{shapes}: \{32x32, 64x64, 96x96, 128x128, 256x256, 320x320, 384x384, 448x448, 512x512, 768x768, 1024x1024, 1536x1536\}
	\item \textbf{cases}:
        \begin{itemize}
			\item gen\_uniform: seeds=1,
			\item gen\_uniform: seeds=2,
			\item gen\_uniform: density=0.0001,
			\item gen\_uniform: density=0.001,
			\item gen\_uniform: density=0.01,
			\item gen\_uniform: density=0.02,
			\item gen\_uniform: density=0.03,
			\item gen\_uniform: density=0.04,
			\item gen\_uniform: density=0.05,
			\item gen\_uniform: density=0.1,
		\end{itemize}
\end{itemize}

>>>>

% kollektiv
% https://www.youtube.com/watch?v=E8g5YrDXg2k
% go with the flow
% https://www.youtube.com/watch?v=DcHKOC64KnE
% private party project
% https://www.youtube.com/watch?v=ckKi01gqW7A&t=878s
% royal blood
% https://www.youtube.com/watch?v=sbx95gBb5HM
% i don't want to sleep
% https://www.youtube.com/watch?v=3oBCu9zywzE
% hehe
% https://www.youtube.com/watch?v=Dii8ZVtR9Tc&t=18s
% gary clark jr
% https://www.youtube.com/watch?v=iAXZmaqknQU

@@

%%% BONUS %%%
%\usepackage[table]{xcolor}  % for colors (like `red`)
\usepackage[normalem]{ulem} % for underline
\usepackage{booktabs}       % for better table
\usepackage{bm}             % for special table cell (`cellcolor`)
\usepackage{hhline,soul}    % for `hl` command (highlight text)
\usepackage{amsmath}        % for multi-line math
\usepackage[bottom]{footmisc}% for footnotes

\usepackage{diagbox} % TABLE MASTERS - section
\usepackage{tabularx, booktabs}
\newcolumntype{L}{>{\raggedright\footnotesize}m{5.75cm}}
\renewcommand{\arraystretch}{1.2}
%%%%%%%%%%%%%

@@

\begin{table}[H] \centering
\begin{tabular}{@{}lllll@{}}
\toprule
\textbf{Reference}                & \textbf{Algorithm}    & \textbf{Exactness}
	& \textbf{Time}         & \textbf{Work}         \\ \midrule
\citep{de2017fast}       & FastGPU      & Exact       & $O(n^3/p)$   & -            \\
\citep{cao2010parallel}  & PBA          & Exact       & $O(n)$       & $O(mN)$      \\
\citep{honda2017simple}  & based on SKW & Exact       & $O(n)$       & $O(N)$       \\
\citep{manduhu2019work}  & WTO          & \cellcolor{blue!25}\textbf{Exact}&
	\cellcolor{blue!25}$\mathbf{O(\log n)}$  & $O(N)$       \\
\citep{schneider2009gpu} & SKW          & Approximate & $O(n)$       & $O(N)$       \\
\citep{rong2006jump}     & JFA          & Approximate & $O(\log n)$  & $O(N\log n)$ \\ \bottomrule
In this paper            & \ourjfasingle&
	\cellcolor{blue!25}\textbf{Approximate} &
	\cellcolor{blue!25}$\sim$$\mathbf{O(\log^{\ast} n)}$ & $\sim$$O(N)$ \\
                         & \ourjfa      &
	\cellcolor{blue!25}\textbf{Approximate} &
	\cellcolor{blue!25}$\sim$$\mathbf{O(1)}$ & $\sim$$O(N)$ \\
\bottomrule
\end{tabular}
\vspace{1em}
\caption{Different GPU algorithms for computing EDT}
\end{table}

@@

KWADRAT TUTAJ????????? (komentarz latex)

\begin{table}[H] \centering
\begin{tabular}{@{}l|ccc@{}}
\toprule
\hspace*{0.175cm}\diagbox{\textbf{Density}}{\textbf{Shape}}
                         & Small (32-128)    & Medium (256-448)   & Large (512-1536)  \\
\midrule
Low ($\rho$=0.00005-0.001)    & Bruteforce           & Bruteforce        & JFA       \\
High ($\rho$=0.01-0.1)        & JFA           & JFA        & JFA       \\
\bottomrule
\end{tabular}
\vspace{1em}
\caption{State-of-the-art for specific domains (before our work).}
\end{table}

% # kwadrat
% #                   small          medium       big
% #    low den.        ?                ?         JFA
% #    high den.       ?                ?          ?

% # [music]
% # https://www.youtube.com/watch?v=78oIolvjIsw

@@

\hl{\textbf{UWAGA}: opisac ze szukamy 4 podprzestrzenie w turach! (moze tez o
nowym wzorku ktory szuka tylko prawidlowych}

@@

\begin{table}[H] \centering
\begin{tabular}{@{}l|ccc@{}}
\toprule
\hspace*{0.175cm}\diagbox{\textbf{Density}}{\textbf{Shape}}
                         & Small (32-128)    & Medium (256-448)   & Large (512-1536)  \\
\midrule
Low ($\rho$=0.00005-0.001)    & JFA           & Blabla        & ?       \\
High ($\rho$=0.01-0.1)        & JFAStar           & ?        & ?       \\
\bottomrule
\end{tabular}
\vspace{1em}
\caption{Found in this paper state-of-the-art for specific domains.}
\end{table}

@@

\begin{itemize}
	\item \textbf{shapes}: \{32x32, 64x64, 96x96, 128x128, 256x256, 320x320, 384x384, 448x448, 512x512, 768x768, 1024x1024, 1536x1536\}
	\item \textbf{cases}:
        \begin{itemize}
			\item gen\_uniform: seeds=1,
			\item gen\_uniform: seeds=3,
			\item gen\_uniform: density=0.0001,
			\item gen\_uniform: density=0.001,
			\item gen\_uniform: density=0.01,
			\item gen\_uniform: density=0.02,
			\item gen\_uniform: density=0.03,
			\item gen\_uniform: density=0.04,
			\item gen\_uniform: density=0.05,
			\item gen\_uniform: density=0.1,
		\end{itemize}
\end{itemize}
